\textbf{Optimization of Porous Silicon Gradient Refractive Index Structures.}

### 2020-06-10 paper.tex
Add a couple of notes
Start to revise experimental details.

The current density normal to the surface may now be obtained as
$j_\perp=-\sigma\partial\phi/\partial z$,
\begin{equation}
  \label{Eq:J}
  \begin{split}
    j_\perp(\bm r) =& -\frac{I}{ab}\biggl(1+{\sum_{\bm G}}'\frac{2\sinh
      Gc}{\sinh 2Gc}\cosh G(c-z_0)\cos G_x x_0 \cos G_y y_0\\
    &\times \cosh Gz\, e^{i\bm G\cdot\bm r_\|}\biggr).
  \end{split}
\end{equation}
Eq. \eqref{Eq:J} is a very rapidly convergent expression that allows,
in particular, to calculate the current $j_\perp(x,y,0)$ that attacks
the substrate to produce the PS sample.
Integrating over the surface of the sample we verify
\begin{equation}
  \label{eq:intj}
  \int_0^adx\int_0^bdy\,j_\perp(\bm r)=-I,
\end{equation}
as the contributions of opposite non-null reciprocal vectors cancel
out. As expected, all of the current that leaves the electrode find
its way to the substrate.

Using Eq. \eqref{Eq:J} we can correlate the local current density at
the sample as it is prepared with its geometric and optical
properties. For the calculation of the optical properties we use the
well known transfer matrix method \notaL{refs}.

\section{Experimental Details}
\begin{figure}
  \centering
  \includegraphics[scale=0.6]{Images/DE1}
\caption{\emph{Schematic of the experimental set-up for
      fabrication of porous silicon with GRIN. (a) Represents an
      outline of the surface section, divided by three regions
      A, B and C, corresponding to High, Medium and Low Porosity
      respectively. (b) It is the diagram of the electrochemical
      cell with its parts: silicon wafer, Teflon cell, platinum
      point electrode, Electrochemical Aqueous solution and the
      connection of the circuit with the cathode and anode. (c)
      It is a schematic drawing of the Cross section of the
      electrochemically attacked porous silicon seen in three
      different regions as mentioned above. }}
    \label{fig:DE1}
  \end{figure}

In the Fig. \ref{fig:DE1} a shows schematic representation of the
experimental setup where porous silicon can be manufactured with GRIN,
taking into account the considerations of the electrode as tip, the
rectangular cell and the sample (silicon wafer) with the largest
rectangular attack area.
In Fig. \ref{fig:DE1} a) we draw an outline of the surface section,
divided by three regions A, B and C, dependes in therir porosity i.e.,
High, Medium and Low Porosity. All this corresponding to  expected to
be obtained in the experiments. Fig. \ref{fig:DE1} b) the scheme shows
the electrochemical cell with its parts: silicon wafer, teflon cell,
platinum point electrode, electrochemical Aqueous Solution and the
connection of the circuit with the cathode and anode. Finally,
Fig. \ref{fig:DE1} c) it is a schematic drawing of the Cross section
of the electrochemically attacked porous silicon seen from three
different regions as mentioned above. In section 3.1 we give the
details used to carry out our experiments.

>>>>

The current density normal to the surface may now be obtained as
$j_\perp=-\sigma\partial\phi/\partial z$,
\begin{equation}
  \label{Eq:J}
  \begin{split}
    j_\perp(\bm r) =& -\frac{I}{ab}\biggl(1+{\sum_{\bm G}}'\frac{2\sinh
      Gc}{\sinh 2Gc}\cosh G(c-z_0)\cos G_x x_0 \cos G_y y_0\\
    &\times \cosh Gz\, e^{i\bm G\cdot\bm r_\|}\biggr).
  \end{split}
\end{equation}
Eq. \eqref{Eq:J} is a very rapidly convergent expression that allows,
in particular, to calculate the current $j_\perp(x,y,0)$ that attacks
the substrate to produce the PS sample.
Integrating over the surface of the sample we verify
\begin{equation}
  \label{eq:intj}
  \int_0^adx\int_0^bdy\,j_\perp(\bm r)=-I,
\end{equation}
as the contributions of opposite non-null reciprocal vectors cancel
out. As expected, all of the current that leaves the electrode find
its way to the substrate.
\notaL{En este sistema, ¿cuál es el cátodo y cuál el ánodo? ¿de dónde
  hacia dónde va la corriente? ¿$q_0$ es positiva o negativa?}

Using Eq. \eqref{Eq:J} we can correlate the local current density at
the sample as it is prepared with its geometric and optical
properties. For the calculation of the optical properties we use the
well known transfer matrix method \notaL{refs}.
\notaL{No necesitamos presentar la teoría de matrices de
  transferencia. No hay nada original ahí.}

\section{Experimental Details}
\begin{figure}
  \centering
  \includegraphics[scale=0.6]{Images/DE1}
\caption{(a) \notaL{reordenar figura} Experimental set-up for
      fabrication of porous silicon with GRIN, consisting of a
      rectangular electrochemical cell. We indicate the Si wafer, the
      teflon cell, the platinum point electrode, the electrolyte and the
      current source. (b) Top and (c) side schematic views of the resulting sample,
      illustrating three regions $A$, $B$ and $C$ of relatively high, medium and
      low porosity respectively illustrating the change gradient in
      pore size and depth. }}
    \label{fig:DE1}
  \end{figure}

Fig. \ref{fig:DE1} shows a schematic representation of our
experimental setup to manufacture porous silicon with GRIN.
\notaL{La figura está feita. Hay un abultamiento extraño en la
  punta. Debería verse el aislamiento y la punta descubierta y más
  sumergida. La letra está demasiado chica. El gradiente de porosidad va
  en la dirección opuesta. El panel (a) tiene una discontinuidad. ¿Tú
  la hiciste o la adaptaste? Usa dos paréntesis (a), (b),
  (c). Alínealos. Pon primero la preparación y luego los resultados
  vistos de arriba y de lado. Está en desorden. Se ve muy descuidada. No dice nada sobre la
  preparación que no esté en la figura 1. Dos páneles no ilustran el
  método experimental, sino el resultado. Quizás yo la quitaría.}
taking into account the considerations of the electrode as tip, the
rectangular cell and the sample (silicon wafer) with the largest
rectangular attack area.

In Fig. \ref{fig:DE1} a) we draw an outline of the surface section,
divided by three regions A, B and C, dependes in therir porosity i.e.,
High, Medium and Low Porosity. All this corresponding to  expected to
be obtained in the experiments. Fig. \ref{fig:DE1} b) the scheme shows
the electrochemical cell with its parts: silicon wafer, teflon cell,
platinum point electrode, electrochemical Aqueous Solution and the
connection of the circuit with the cathode and anode. Finally,
Fig. \ref{fig:DE1} c) it is a schematic drawing of the Cross section
of the electrochemically attacked porous silicon seen from three
different regions as mentioned above. In section 3.1 we give the
details used to carry out our experiments.
